Modelling BCG vaccination in the UK

### 2019-08-08 rmds/05-evidence-policy-change.Rmd
sutherland tweaks

I recreated a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigated scenarios considered by the Joint Committee on Vaccination and Immunisation, and explored new approaches using notification data (see Chapter \@ref(data)). I estimated the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/624916] supervised by Hannah Christensen and Ellen Brooks-Pollock.

@@

In 1987, an assessment of the school-age vaccination program was carried out in England and Wales.[@Sutherland1989] This study was used, combined with a sensitivity analysis of notification rates, as supporting evidence by the Joint Committee on Vaccination and Immunisation (JCVI) BCG subgroup for the change in vaccination policy.[@JVCIBCG2002; @JVCIBCG2003] This chapter aims to re-evaluate this modelling, and re-estimate the predicted impact of stopping the schools scheme.

>>>>

I recreated a previous approach for estimating the impact of ending the BCG schools scheme in England and Wales, updating the model with parameter uncertainty, and measurement error. I investigated scenarios considered by the Joint Committee on Vaccination and Immunisation (JCVI), and explored new approaches using notification data (see Chapter \@ref(data)). I estimated the number of vaccines needed to prevent a single notification, and the average annual additional notifications caused by ending the BCG schools’ scheme. This work was adapted from a preprint^[Preprint: https://doi.org/10.1101/624916] supervised by Hannah Christensen and Ellen Brooks-Pollock.

@@

In 1987, an assessment of the school-age vaccination program was carried out in England and Wales.[@Sutherland1989] This study was used, combined with a sensitivity analysis of notification rates, as supporting evidence by the JCVI BCG subgroup for the change in vaccination policy.[@JVCIBCG2002; @JVCIBCG2003] This chapter aims to re-evaluate this modelling, and re-estimate the predicted impact of stopping the schools scheme.
